\begin{resume}

  \resumeitem{个人简历}

  1990~年~4~月~17~日出生于山东省淄博市。

  2009~年~9~月考入吉林大学计算机科学与技术专业，2013~年~7~月本科毕业并获得学士学位。

  2013~年~9~月考入清华大学计算机科学与技术系攻读工学博士至今。
  
  
  2016~年~10~月－  2017~年~9~月美国乔治华盛顿大学访问学者。

  \resumeitem{发表的学术论文} % 发表的和录用的合在一起
  
\begin{enumerate}[{[}1{]}]
\item \textbf{Zhang H}, Shi X, Guo Y, et al. Efficient Scheduling of Weighted Coflows in Data Centers. s, 2017.(SCI检索,CCF A类期刊，审稿中).
\item \textbf{Zhang H}., Shi, X., Guo, Y., Wang, Z., \& Yin, X. (2017). More load, more differentiation—Let more flows finish before deadline in data center networks. Computer Networks, 127, 352-367.7. (SCI检索,CCF B类期刊).
\item \textbf{Zhang H}, Shi, X., Yin, X.,  \& Wang, Z. (2017, October). Joint source selection and transfer optimization for erasure coding storage system. In 2017 IEEE/ACM 36th International Performance Computing and Communications Conference(IPCCC).  (pp. 1-10). IEEE.(EI检索,CCF C类会议)
\item \textbf{Zhang H}., Shi, X., Yin, X.,  \& Wang, Z. (2017, October). Yosemite: Efficient scheduling of weighted coflows in data centers. In 2017 IEEE 25th International Conference on Network Protocols (ICNP) (pp. 1-2). IEEE..(EI检索,CCF B类 poster)
\item \textbf{Zhang H}, Shi, X., Yin, X., Wang, Z.,  \& Guo, Y. (2016, June). FDRC-Flow duration time based rate control in data center networks. In Quality of Service (IWQoS), 2016 IEEE/ACM 24th International Symposium on (pp. 1-10). IEEE..(EI检索,CCF B类会议)
\item \textbf{Zhang H}, Shi, X., Yin, X., Ren, F., \&Wang, Z. (2015, April). More load, more differentiation—A design principle for deadline-aware congestion control. In Computer Communications (INFOCOM), 2015 IEEE Conference on (pp. 127-135). IEEE. .(EI检索,CCF A类会议)
 \item  Geng, H., Shi, X., Yin, X., Wang, Z., \&  \textbf{Zhang H}. (2015, June). Algebra and algorithms for efficient and correct multipath QoS routing in link state networks. In Quality of Service (IWQoS), 2015 IEEE 23rd International Symposium on (pp. 261-266). IEEE.  (EI检索,CCF B类会议)
\item Zhao, Z., Li, Q., Xu, M., Shi, X.,  \&  \textbf{Zhang H}. (2016, May). Reduce completion time and guarantee throughput by transport with slight congestion. In Communications (ICC), 2016 IEEE International Conference on (pp. 1-6). IEEE.(EI检索,CCF C类会议)
\end{enumerate}


\resumeitem{参与的科研项目}
\begin{enumerate}[{[}1{]}]
\item 清华-思科联合实验室项目，``OnePK based Network Traffic Data Collection and Analysis"
\item 清华-思科联合实验室项目，``Data Center Traffic Generator"
\item 863项目，``软件定义网络（ SDN）验证与示范"

\end{enumerate}
\end{resume}
